\ttitle

### 2015-08-27 Appendices/AppendixExcelMacros.tex
Review - Minor changes to Appendices
- Modify short title
- insert \clearpage
Access VBA code added
- I think this officially completes this thesis

% Appendix A

\chapter{Visual Basic for Applications For CPET Analysis} % Main appendix title

\label{AppendixExcelMacros} % For referencing this appendix elsewhere, use \ref{AppendixA}

\lhead{Appendix B. \emph{Excel VBA For CPET Analysis}} % This is for the header on each page - perhaps a shortened title

@@

   For Each ws In Worksheets
     If ws.Range("$B$1").Value = "" Then
       Exit Sub
     End If
     If ws.Name <> "aaa_main" Then
       strName = Split(CStr(ws.Range("$B$1").Value), "(")
       ws.Name = LCase(strName(0))
       ws.Activate
       ws.Range("B4").Select
       ActiveWindow.FreezePanes = True
     End If
   Next ws

@@

   SortDescending = False

   If ActiveWindow.SelectedSheets.Count = 1 Then
     'Change the 1 to the worksheet you want sorted first
     FirstWSToSort = 1
     LastWSToSort = Worksheets.Count
    Else
     With ActiveWindow.SelectedSheets
       For N = 2 To .Count
         If .Item(N - 1).Index <> .Item(N).Index - 1 Then
           MsgBox "You cannot sort non-adjacent sheets"
           Exit Sub
         End If
       Next N

       FirstWSToSort = .Item(1).Index
       LastWSToSort = .Item(.Count).Index
     End With
   End If

   For M = FirstWSToSort To LastWSToSort
     For N = M To LastWSToSort
       If SortDescending = True Then
         If UCase(Worksheets(N).Name) > UCase(Worksheets(M).Name) Then
           Worksheets(N).Move Before:=Worksheets(M)
         End If
       Else
         If UCase(Worksheets(N).Name) < UCase(Worksheets(M).Name) Then
           Worksheets(N).Move Before:=Worksheets(M)
         End If
       End If
     Next N
   Next M

   Dim x As Integer
   x = 2
   Sheets("aaa_main").Range("A:A").Clear
   Sheets("aaa_main").Cells(1, 1) = "SheetName"
   For Each ws In Worksheets
     Sheets("aaa_main").Cells(x, 1) = ws.Name
     x = x + 1
   Next ws
End Sub

Sub GotoSheet()
  If ActiveWindow.ActiveSheet.Name = "aaa_main" Then
    Dim selName As String
    selName = ActiveWindow.ActiveCell.Value
    Worksheets(selName).Activate
  Else
    Worksheets("aaa_main").Activate
  End If
End Sub

Sub VCO2VO2()
  Dim ws As Worksheet
  For Each ws In Worksheets
    Dim x As Integer
    x = 4
    While ws.Cells(x, 2) > 0
      If ws.Cells(x, 9) <> "-" And ws.Cells(x, 6) <> "-" Then
        ws.Cells(x, 22) = CDbl(ws.Cells(x, 9)) / CDbl(ws.Cells(x, 6))
      End If
      x = x + 1
    Wend
  Next ws  
End Sub

Sub ClearColumn()
  Dim ws As Worksheet
  For Each ws In Worksheets
    ws.Range("AD9") = ws.Range("A1")
    ws.Range("A1").Clear
  Next ws
End Sub

@@

Sub AddRCValues()
  Dim x As Integer
  For x = 3 To 88
    Sheets(Sheets("aaa_main").Cells(x, 1).Value).Range("AD8") = _
      Sheets("aaa_main").Cells(x, 27).Value
    Sheets(Sheets("aaa_main").Cells(x, 1).Value).Range("AD9") = _
      Sheets("aaa_main").Cells(x, 28).Value
  Next x
End Sub

Sub CopyLineForSPSS()
  Dim rng As Range
  Dim selrow As Integer
  Dim selrng As String  
  selrow = ActiveWindow.ActiveCell.Row
  selrng = "AF" & CStr(selrow) & ":BX" & CStr(selrow)
  Range(selrng).Select
  Selection.Copy
End Sub

%----------------------------------
Sub ValuesAT()
  Dim r As Integer
  r = 3 - Selection.Cells(1, 1).Row
  ActiveSheet.Range("X29") = Selection.Cells(r, 1)
  ActiveSheet.Range("Y29") = Selection.Cells(r, 3)
  ActiveSheet.Range("Z29") = Selection.Cells(r, 4) 'VE
  ActiveSheet.Range("AA29") = Selection.Cells(r, 5) 'VT
  ActiveSheet.Range("AB29") = Selection.Cells(r, 6) 'VO2
  ActiveSheet.Range("AC29") = Selection.Cells(r, 7) 'VO2/KG
  ActiveSheet.Range("AD29") = Selection.Cells(r, 8) 'VE/VO2
  ActiveSheet.Range("AE29") = Selection.Cells(r, 9) 'VCO2
  ActiveSheet.Range("AF29") = Selection.Cells(r, 10) 'VE/VCO2
  ActiveSheet.Range("AG29") = Selection.Cells(r, 11) 'RER
  ActiveSheet.Range("AH29") = Selection.Cells(r, 12) 'PETO2
  ActiveSheet.Range("AI29") = Selection.Cells(r, 13) 'PETCO2
  ActiveSheet.Range("AJ29") = Selection.Cells(r, 14) 'O2PULSE
  ActiveSheet.Range("AK29") = Selection.Cells(r, 15) 'HR
  ActiveSheet.Range("AL29") = Selection.Cells(r, 16) 'Bf

  ActiveSheet.Range("W30") = "AT"
  ActiveSheet.Range("X30") = WorksheetFunction.Average(Selection.Columns(1)) 'TIME
  ActiveSheet.Range("Y30") = WorksheetFunction.Average(Selection.Columns(3)) 'LOAD
  ActiveSheet.Range("Z30") = WorksheetFunction.Average(Selection.Columns(4)) 'VE
  ActiveSheet.Range("AA30") = WorksheetFunction.Average(Selection.Columns(5)) 'VT
  ActiveSheet.Range("AB30") = WorksheetFunction.Average(Selection.Columns(6)) 'VO2
  ActiveSheet.Range("AC30") = WorksheetFunction.Average(Selection.Columns(7)) 'VO2/KG
  ActiveSheet.Range("AD30") = WorksheetFunction.Average(Selection.Columns(8)) 'VE/VO2
  ActiveSheet.Range("AE30") = WorksheetFunction.Average(Selection.Columns(9)) 'VCO2
  ActiveSheet.Range("AF30") = WorksheetFunction.Average(Selection.Columns(10)) 'VE/VCO2
  ActiveSheet.Range("AG30") = WorksheetFunction.Average(Selection.Columns(11)) 'RER
  ActiveSheet.Range("AH30") = WorksheetFunction.Average(Selection.Columns(12)) 'PETO2
  ActiveSheet.Range("AI30") = WorksheetFunction.Average(Selection.Columns(13)) 'PETCO2
  ActiveSheet.Range("AJ30") = WorksheetFunction.Average(Selection.Columns(14)) 'O2PULSE
  ActiveSheet.Range("AK30") = WorksheetFunction.Average(Selection.Columns(15)) 'HR
  ActiveSheet.Range("AL30") = WorksheetFunction.Average(Selection.Columns(16)) 'Bf
End Sub

Sub ValuesPeak()
  ActiveSheet.Range("W31") = "Peak"
  ActiveSheet.Range("X31") = WorksheetFunction.Average(Selection.Columns(1)) 'TIME
  ActiveSheet.Range("Y31") = WorksheetFunction.Max(Selection.Columns(3)) 'LOAD
  ActiveSheet.Range("Z31") = WorksheetFunction.Max(Selection.Columns(4)) 'VE
  ActiveSheet.Range("AA31") = WorksheetFunction.Max(Selection.Columns(5)) 'VT
  ActiveSheet.Range("AB31") = WorksheetFunction.Max(Selection.Columns(6)) 'VO2
  ActiveSheet.Range("AC31") = WorksheetFunction.Max(Selection.Columns(7)) 'VO2/KG
  ActiveSheet.Range("AD31") = WorksheetFunction.Max(Selection.Columns(8)) 'VE/VO2
  ActiveSheet.Range("AE31") = WorksheetFunction.Max(Selection.Columns(9)) 'VCO2
  ActiveSheet.Range("AF31") = WorksheetFunction.Max(Selection.Columns(10)) 'VE/VCO2
  ActiveSheet.Range("AG31") = WorksheetFunction.Max(Selection.Columns(11)) 'RER
  ActiveSheet.Range("AH31") = WorksheetFunction.Max(Selection.Columns(12)) 'PETO2
  ActiveSheet.Range("AI31") = WorksheetFunction.Max(Selection.Columns(13)) 'PETCO2
  ActiveSheet.Range("AJ31") = WorksheetFunction.Max(Selection.Columns(14)) 'O2PULSE
  ActiveSheet.Range("AK31") = WorksheetFunction.Max(Selection.Columns(15)) 'HR
  ActiveSheet.Range("AL31") = WorksheetFunction.Max(Selection.Columns(16)) 'Bf
End Sub

Sub ValuesOther()
  ActiveSheet.Range("W32") = "Other"
  ActiveSheet.Range("X32") = WorksheetFunction.Average(Selection.Columns(1)) 'TIME
  ActiveSheet.Range("Y32") = WorksheetFunction.Average(Selection.Columns(3)) 'LOAD
  ActiveSheet.Range("Z32") = WorksheetFunction.Average(Selection.Columns(4)) 'VE
  ActiveSheet.Range("AA32") = WorksheetFunction.Average(Selection.Columns(5)) 'VT
  ActiveSheet.Range("AB32") = WorksheetFunction.Average(Selection.Columns(6)) 'VO2
  ActiveSheet.Range("AC32") = WorksheetFunction.Average(Selection.Columns(7)) 'VO2/KG
  ActiveSheet.Range("AD32") = WorksheetFunction.Average(Selection.Columns(8)) 'VE/VO2
  ActiveSheet.Range("AE32") = WorksheetFunction.Average(Selection.Columns(9)) 'VCO2
  ActiveSheet.Range("AF32") = WorksheetFunction.Average(Selection.Columns(10)) 'VE/VCO2
  ActiveSheet.Range("AG32") = WorksheetFunction.Average(Selection.Columns(11)) 'RER
  ActiveSheet.Range("AH32") = WorksheetFunction.Average(Selection.Columns(12)) 'PETO2
  ActiveSheet.Range("AI32") = WorksheetFunction.Average(Selection.Columns(13)) 'PETCO2
  ActiveSheet.Range("AJ32") = WorksheetFunction.Average(Selection.Columns(14)) 'O2PULSE
  ActiveSheet.Range("AK32") = WorksheetFunction.Average(Selection.Columns(15)) 'HR
  ActiveSheet.Range("AL32") = WorksheetFunction.Average(Selection.Columns(16)) 'Bf
End Sub

Sub AutomatePeakOtherValues()
  Dim ws As Worksheet
  Dim topRow As Integer
  Dim bottomRow As Integer
  For Each ws In Worksheets
    If ws.Name <> "aaa_main" Then
      ws.Activate
      'Fill other values
      Dim rng As Range
      Dim fdrng As Range
      Set rng = ws.Range("C:C")
      Set fdrng = rng.Find(30, LookIn:=xlValues)
      If Not fdrng Is Nothing Then
        topRow = fdrng(0, 1).Row
        bottomRow = fdrng(2, 0).Row
        Set rng = ws.Range(topRow & ":" & bottomRow)
        rng.Select
        Call ValuesOther
      End If

      'Fill peak values
      Dim maxVO2
      maxVO2 = WorksheetFunction.Max(ws.Range("G:G"))
      Set rng = ws.Range("G:G")
      Set fdrng = rng.Find(maxVO2)
        If Not fdrng Is Nothing Then
          topRow = fdrng(-1, 1).Row
          bottomRow = fdrng(3, 0).Row
        If ws.Range("W31").Value = "" Then
          Set rng = ws.Range(topRow & ":" & bottomRow)
          rng.Select
          Call ValuesPeak
        End If
      End If

@@

Sub VECharts()
  Dim ws As Worksheet
  For Each ws In Worksheets
    With ws.ChartObjects.Add _
      (Left:=800, Top:=725, Width:=400, Height:=225)
      .chart.ChartType = xlLine
      .chart.SetSourceData Source:=ws.Range("A:A,H:H,J:J") _
      , PlotBy:=xlColumns

      .chart.HasAxis(xlCategory, xlPrimary) = True
      .chart.HasAxis(xlValue, xlPrimary) = True

      .chart.Axes(xlCategory, xlPrimary).CategoryType = xlAutomatic
    End With
  Next ws
End Sub

Sub CopyCPETParametersFromSheetsToMain()
  Dim x As Integer
  For x = 3 To 99
    Dim sheetname As String
    Sheets("aaa_main").Activate
    sheetname = ActiveSheet.Cells(x, 1)
    ActiveSheet.Cells(x, 32).Select
    Sheets(sheetname).Select
    Range("X30:AL30").Select
    Selection.Copy
    Sheets("aaa_main").Select
    ActiveSheet.Paste

@@

Sub CopyVEVO2VEVCO2FromSheetsToMain()
  Dim x As Integer
  For x = 3 To 99
    Dim sheetname As String
    Sheets("aaa_main").Activate
    sheetname = ActiveSheet.Cells(x, 1)
    ActiveSheet.Cells(x, 79).Select
    Sheets(sheetname).Select
    Range("Y22").Select
    Selection.Copy
    Sheets("aaa_main").Select
    ActiveSheet.Paste

@@

Sub FindStartEndTimeofExercise()
  Dim x As Integer
  Dim y As Integer
  Dim starttime As String
  Dim endtime As String
  Dim sheetname As String
  For x = 3 To 99
    Sheets("aaa_main").Activate
    sheetname = ActiveSheet.Cells(x, 1)
    Sheets(sheetname).Select
    y = 15
    While ActiveSheet.Cells(y, 3) = "-"
      y = y + 1
    Wend
    starttime = ActiveSheet.Cells(y, 1)
    y = y + 5
    While ActiveSheet.Cells(y, 3) > "0"
      y = y + 1
    Wend
    endtime = ActiveSheet.Cells(y - 1, 1)
    Sheets("aaa_main").Activate
    ActiveSheet.Cells(x, 77) = starttime
    ActiveSheet.Cells(x, 78) = endtime
  Next x
End Sub

>>>>

\chapter{Visual Basic for Applications For CPET Analysis} % Main appendix title
\label{AppendixExcelMacros} % For referencing this appendix elsewhere, use \ref{AppendixA}
\lhead{Appendix \ref{AppendixExcelMacros}. \emph{Excel VBA For CPET Analysis}} % This is for the header on each page - perhaps a shortened title
\clearpage
%------------------------------------------

@@

   For Each ws In Worksheets
     If ws.Range("$B$1").Value="" Then
       Exit Sub
     End If
     If ws.Name <> "aaa_main" Then
       strName=Split(CStr(ws.Range("$B$1").Value), "(")
       ws.Name=LCase(strName(0))
       ws.Activate
       ws.Range("B4").Select
       ActiveWindow.FreezePanes=True
     End If
   Next ws

@@

   SortDescending=False

   If ActiveWindow.SelectedSheets.Count=1 Then
     'Change the 1 to the worksheet you want sorted first
     FirstWSToSort=1
     LastWSToSort=Worksheets.Count
    Else
     With ActiveWindow.SelectedSheets
       For N=2 To .Count
         If .Item(N - 1).Index <> .Item(N).Index - 1 Then
           MsgBox "You cannot sort non-adjacent sheets"
           Exit Sub
         End If
       Next N

       FirstWSToSort=.Item(1).Index
       LastWSToSort=.Item(.Count).Index
     End With
   End If

   For M=FirstWSToSort To LastWSToSort
     For N=M To LastWSToSort
       If SortDescending=True Then
         If UCase(Worksheets(N).Name) > UCase(Worksheets(M).Name) Then
           Worksheets(N).Move Before:=Worksheets(M)
         End If
       Else
         If UCase(Worksheets(N).Name) < UCase(Worksheets(M).Name) Then
           Worksheets(N).Move Before:=Worksheets(M)
         End If
       End If
     Next N
   Next M

   Dim x As Integer
   x=2
   Sheets("aaa_main").Range("A:A").Clear
   Sheets("aaa_main").Cells(1, 1)="SheetName"
   For Each ws In Worksheets
     Sheets("aaa_main").Cells(x, 1)=ws.Name
     x=x + 1
   Next ws
End Sub

Sub GotoSheet()
  If ActiveWindow.ActiveSheet.Name="aaa_main" Then
    Dim selName As String
    selName=ActiveWindow.ActiveCell.Value
    Worksheets(selName).Activate
  Else
    Worksheets("aaa_main").Activate
  End If
End Sub

Sub VCO2VO2()
  Dim ws As Worksheet
  For Each ws In Worksheets
    Dim x As Integer
    x=4
    While ws.Cells(x, 2) > 0
      If ws.Cells(x, 9) <> "-" And ws.Cells(x, 6) <> "-" Then
        ws.Cells(x, 22)=CDbl(ws.Cells(x, 9)) / CDbl(ws.Cells(x, 6))
      End If
      x=x + 1
    Wend
  Next ws  
End Sub

Sub ClearColumn()
  Dim ws As Worksheet
  For Each ws In Worksheets
    ws.Range("AD9")=ws.Range("A1")
    ws.Range("A1").Clear
  Next ws
End Sub

@@

Sub AddRCValues()
  Dim x As Integer
  For x=3 To 88
    Sheets(Sheets("aaa_main").Cells(x, 1).Value).Range("AD8")=_
      Sheets("aaa_main").Cells(x, 27).Value
    Sheets(Sheets("aaa_main").Cells(x, 1).Value).Range("AD9")=_
      Sheets("aaa_main").Cells(x, 28).Value
  Next x
End Sub

Sub CopyLineForSPSS()
  Dim rng As Range
  Dim selrow As Integer
  Dim selrng As String  
  selrow=ActiveWindow.ActiveCell.Row
  selrng="AF" & CStr(selrow) & ":BX" & CStr(selrow)
  Range(selrng).Select
  Selection.Copy
End Sub

%----------------------------------
Sub ValuesAT()
  Dim r As Integer
  r=3 - Selection.Cells(1, 1).Row
  ActiveSheet.Range("X29")=Selection.Cells(r, 1)
  ActiveSheet.Range("Y29")=Selection.Cells(r, 3)
  ActiveSheet.Range("Z29")=Selection.Cells(r, 4)'VE
  ActiveSheet.Range("AA29")=Selection.Cells(r, 5)'VT
  ActiveSheet.Range("AB29")=Selection.Cells(r, 6)'VO2
  ActiveSheet.Range("AC29")=Selection.Cells(r, 7)'VO2/KG
  ActiveSheet.Range("AD29")=Selection.Cells(r, 8)'VE/VO2
  ActiveSheet.Range("AE29")=Selection.Cells(r, 9)'VCO2
  ActiveSheet.Range("AF29")=Selection.Cells(r, 10)'VE/VCO2
  ActiveSheet.Range("AG29")=Selection.Cells(r, 11)'RER
  ActiveSheet.Range("AH29")=Selection.Cells(r, 12)'PETO2
  ActiveSheet.Range("AI29")=Selection.Cells(r, 13)'PETCO2
  ActiveSheet.Range("AJ29")=Selection.Cells(r, 14)'O2PULSE
  ActiveSheet.Range("AK29")=Selection.Cells(r, 15)'HR
  ActiveSheet.Range("AL29")=Selection.Cells(r, 16)'Bf

  ActiveSheet.Range("W30")="AT"
  ActiveSheet.Range("X30")=WorksheetFunction.Average(Selection.Columns(1))'TIME
  ActiveSheet.Range("Y30")=WorksheetFunction.Average(Selection.Columns(3))'LOAD
  ActiveSheet.Range("Z30")=WorksheetFunction.Average(Selection.Columns(4))'VE
  ActiveSheet.Range("AA30")=WorksheetFunction.Average(Selection.Columns(5))'VT
  ActiveSheet.Range("AB30")=WorksheetFunction.Average(Selection.Columns(6))'VO2
  ActiveSheet.Range("AC30")=WorksheetFunction.Average(Selection.Columns(7))'VO2/KG
  ActiveSheet.Range("AD30")=WorksheetFunction.Average(Selection.Columns(8))'VE/VO2
  ActiveSheet.Range("AE30")=WorksheetFunction.Average(Selection.Columns(9))'VCO2
  ActiveSheet.Range("AF30")=WorksheetFunction.Average(Selection.Columns(10))'VE/VCO2
  ActiveSheet.Range("AG30")=WorksheetFunction.Average(Selection.Columns(11))'RER
  ActiveSheet.Range("AH30")=WorksheetFunction.Average(Selection.Columns(12))'PETO2
  ActiveSheet.Range("AI30")=WorksheetFunction.Average(Selection.Columns(13))'PETCO2
  ActiveSheet.Range("AJ30")=WorksheetFunction.Average(Selection.Columns(14))'O2PULSE
  ActiveSheet.Range("AK30")=WorksheetFunction.Average(Selection.Columns(15))'HR
  ActiveSheet.Range("AL30")=WorksheetFunction.Average(Selection.Columns(16))'Bf
End Sub

Sub ValuesPeak()
  ActiveSheet.Range("W31")="Peak"
  ActiveSheet.Range("X31")=WorksheetFunction.Average(Selection.Columns(1))'TIME
  ActiveSheet.Range("Y31")=WorksheetFunction.Max(Selection.Columns(3))'LOAD
  ActiveSheet.Range("Z31")=WorksheetFunction.Max(Selection.Columns(4))'VE
  ActiveSheet.Range("AA31")=WorksheetFunction.Max(Selection.Columns(5))'VT
  ActiveSheet.Range("AB31")=WorksheetFunction.Max(Selection.Columns(6))'VO2
  ActiveSheet.Range("AC31")=WorksheetFunction.Max(Selection.Columns(7))'VO2/KG
  ActiveSheet.Range("AD31")=WorksheetFunction.Max(Selection.Columns(8))'VE/VO2
  ActiveSheet.Range("AE31")=WorksheetFunction.Max(Selection.Columns(9))'VCO2
  ActiveSheet.Range("AF31")=WorksheetFunction.Max(Selection.Columns(10))'VE/VCO2
  ActiveSheet.Range("AG31")=WorksheetFunction.Max(Selection.Columns(11))'RER
  ActiveSheet.Range("AH31")=WorksheetFunction.Max(Selection.Columns(12))'PETO2
  ActiveSheet.Range("AI31")=WorksheetFunction.Max(Selection.Columns(13))'PETCO2
  ActiveSheet.Range("AJ31")=WorksheetFunction.Max(Selection.Columns(14))'O2PULSE
  ActiveSheet.Range("AK31")=WorksheetFunction.Max(Selection.Columns(15))'HR
  ActiveSheet.Range("AL31")=WorksheetFunction.Max(Selection.Columns(16))'Bf
End Sub

Sub ValuesOther()
  ActiveSheet.Range("W32")="Other"
  ActiveSheet.Range("X32")=WorksheetFunction.Average(Selection.Columns(1))'TIME
  ActiveSheet.Range("Y32")=WorksheetFunction.Average(Selection.Columns(3))'LOAD
  ActiveSheet.Range("Z32")=WorksheetFunction.Average(Selection.Columns(4))'VE
  ActiveSheet.Range("AA32")=WorksheetFunction.Average(Selection.Columns(5))'VT
  ActiveSheet.Range("AB32")=WorksheetFunction.Average(Selection.Columns(6))'VO2
  ActiveSheet.Range("AC32")=WorksheetFunction.Average(Selection.Columns(7))'VO2/KG
  ActiveSheet.Range("AD32")=WorksheetFunction.Average(Selection.Columns(8))'VE/VO2
  ActiveSheet.Range("AE32")=WorksheetFunction.Average(Selection.Columns(9))'VCO2
  ActiveSheet.Range("AF32")=WorksheetFunction.Average(Selection.Columns(10))'VE/VCO2
  ActiveSheet.Range("AG32")=WorksheetFunction.Average(Selection.Columns(11))'RER
  ActiveSheet.Range("AH32")=WorksheetFunction.Average(Selection.Columns(12))'PETO2
  ActiveSheet.Range("AI32")=WorksheetFunction.Average(Selection.Columns(13))'PETCO2
  ActiveSheet.Range("AJ32")=WorksheetFunction.Average(Selection.Columns(14))'O2PULSE
  ActiveSheet.Range("AK32")=WorksheetFunction.Average(Selection.Columns(15))'HR
  ActiveSheet.Range("AL32")=WorksheetFunction.Average(Selection.Columns(16))'Bf
End Sub

Sub AutomatePeakOtherValues()
  Dim ws As Worksheet
  Dim topRow As Integer
  Dim bottomRow As Integer
  For Each ws In Worksheets
    If ws.Name <> "aaa_main" Then
      ws.Activate
      'Fill other values
      Dim rng As Range
      Dim fdrng As Range
      Set rng=ws.Range("C:C")
      Set fdrng=rng.Find(30, LookIn:=xlValues)
      If Not fdrng Is Nothing Then
        topRow=fdrng(0, 1).Row
        bottomRow=fdrng(2, 0).Row
        Set rng=ws.Range(topRow & ":" & bottomRow)
        rng.Select
        Call ValuesOther
      End If

      'Fill peak values
      Dim maxVO2
      maxVO2=WorksheetFunction.Max(ws.Range("G:G"))
      Set rng=ws.Range("G:G")
      Set fdrng=rng.Find(maxVO2)
        If Not fdrng Is Nothing Then
          topRow=fdrng(-1, 1).Row
          bottomRow=fdrng(3, 0).Row
        If ws.Range("W31").Value="" Then
          Set rng=ws.Range(topRow & ":" & bottomRow)
          rng.Select
          Call ValuesPeak
        End If
      End If

@@

Sub VECharts()
  Dim ws As Worksheet
  For Each ws In Worksheets
    With ws.ChartObjects.Add _
      (Left:=800, Top:=725, Width:=400, Height:=225)
      .chart.ChartType=xlLine
      .chart.SetSourceData Source:=ws.Range("A:A,H:H,J:J") _
      , PlotBy:=xlColumns

      .chart.HasAxis(xlCategory, xlPrimary)=True
      .chart.HasAxis(xlValue, xlPrimary)=True

      .chart.Axes(xlCategory, xlPrimary).CategoryType=xlAutomatic
    End With
  Next ws
End Sub

Sub CopyCPETParametersFromSheetsToMain()
  Dim x As Integer
  For x=3 To 99
    Dim sheetname As String
    Sheets("aaa_main").Activate
    sheetname=ActiveSheet.Cells(x, 1)
    ActiveSheet.Cells(x, 32).Select
    Sheets(sheetname).Select
    Range("X30:AL30").Select
    Selection.Copy
    Sheets("aaa_main").Select
    ActiveSheet.Paste

@@

Sub CopyVEVO2VEVCO2FromSheetsToMain()
  Dim x As Integer
  For x=3 To 99
    Dim sheetname As String
    Sheets("aaa_main").Activate
    sheetname=ActiveSheet.Cells(x, 1)
    ActiveSheet.Cells(x, 79).Select
    Sheets(sheetname).Select
    Range("Y22").Select
    Selection.Copy
    Sheets("aaa_main").Select
    ActiveSheet.Paste

@@

Sub FindStartEndTimeofExercise()
  Dim x As Integer
  Dim y As Integer
  Dim starttime As String
  Dim endtime As String
  Dim sheetname As String
  For x=3 To 99
    Sheets("aaa_main").Activate
    sheetname=ActiveSheet.Cells(x, 1)
    Sheets(sheetname).Select
    y=15
    While ActiveSheet.Cells(y, 3)="-"
      y=y + 1
    Wend
    starttime=ActiveSheet.Cells(y, 1)
    y=y + 5
    While ActiveSheet.Cells(y, 3) > "0"
      y=y + 1
    Wend
    endtime=ActiveSheet.Cells(y - 1, 1)
    Sheets("aaa_main").Activate
    ActiveSheet.Cells(x, 77)=starttime
    ActiveSheet.Cells(x, 78)=endtime
  Next x
End Sub
